---
title: "Vehicle Collision"
author: "Wangzhi Ll"
date: "11/15/2019"
output: html_document
---

## Setup and Load Data

```{r setup}
library(tidyverse)
#library(extracat)
library(mapdeck)
library(plotly)
library(ggmap)
library(sf)
library(tmap)
library(leaflet)
Sys.setenv("plotly_username"="SafeguardLi")
Sys.setenv("plotly_api_key"="JDJpqet5WWuBC3kDQaQc")
```

```{r loaddata}
data <- read.csv("Motor_Vehicle_Collisions_-_Crashes.csv", header=T, na.strings=c("","NA"))
data_20172018 = data[substr(data$ACCIDENT.DATE,7,10)=='2017'|substr(data$ACCIDENT.DATE,7,10)=='2018',]
crash <- data_20172018%>%select(COLLISION_ID, ACCIDENT.DATE, ACCIDENT.TIME, lat = LATITUDE, lon = LONGITUDE, LOCATION, ON.STREET.NAME, OFF.STREET.NAME, NUMBER.OF.PERSONS.INJURED, NUMBER.OF.PERSONS.KILLED, NUMBER.OF.PEDESTRIANS.INJURED, NUMBER.OF.PEDESTRIANS.KILLED, NUMBER.OF.CYCLIST.INJURED, NUMBER.OF.CYCLIST.KILLED, NUMBER.OF.MOTORIST.INJURED, NUMBER.OF.MOTORIST.KILLED)

crash$ACCIDENT.DATE <- as.Date(crash$ACCIDENT.DATE, "%m/%d/%Y")

crash <- crash%>%mutate(victims = NUMBER.OF.PERSONS.INJURED+NUMBER.OF.PERSONS.KILLED, date = paste(as.character(ACCIDENT.DATE),as.character(ACCIDENT.TIME)))
crash$date <- as.POSIXct(crash$date, "%Y-%m-%d %H:%M", tz = "GMT")
crash <- crash[order(crash$date),]
crash$ON.STREET.NAME <- as.character(crash$ON.STREET.NAME)
crash$OFF.STREET.NAME <- as.character(crash$OFF.STREET.NAME)

# sf
sf <- sf::st_as_sf( crash[!is.na(crash$lat),], coords = c("lon", "lat"))
attr( sf[["geometry"]], "bbox") <- c(xmin = -74.257159, ymin = 40.495992, xmax = -73.699215,ymax= 40.915568)
sf <- sf::st_as_sf( crash[!is.na(crash$lat),], coords = c("lon", "lat"))
```

```{r write_sf}
t1 = Sys.time()
victim <- crash
victim <- victim[which(victim$victims != 0),]
victim_dist <- victim[which(victim$victims == 1),]
max(victim$victims)
for(i in 2:max(victim$victims)){
  temp = victim[which(victim$victims == i),]
  if(dim(temp)[1]!=0){
    for(j in 1:i){
      victim_dist <- rbind(victim_dist, temp)
      print(paste("i:",i,"_j:",j,"_",dim(victim_dist)))
  }  
  }
}
print(paste("Time Use:",Sys.time()-t1))
write_csv(victim_dist,gsub(" ","",paste(getwd(),"/victim.csv")))
```


```{r read_sf}
victim_dist <- read_csv(gsub(" ","",paste(getwd(),"/victim.csv")))
victim_dist <- sf::st_as_sf(victim_dist[!is.na(victim_dist$lat),], coords = c("lon", "lat"))
attr(victim_dist[["geometry"]], "bbox") <- c(xmin = -74.257159, ymin = 40.495992, xmax = -73.699215,ymax= 40.915568)
```

## EDA 

### Missing Value
```{r missing}
visna(crash, sort = "b")
missingLOC <- sum(is.na(crash$LOCATION))/nrow(crash)
fillingSTR <- sum(!is.na(crash$ON.STREET.NAME)&is.na(crash$LOCATION))/nrow(crash)
print(missingLOC - fillingSTR)
```


```{r accident number}
date <- as.data.frame(summary(data$ACCIDENT.DATE))
date$date <- rownames(date)
date$date <- as.character(date$date)
date$date <- as.Date(date$date, "%m/%d/%Y")
date2 <- date[order(date$date),]
ggplot(data = date, aes(y = `summary(data$ACCIDENT.DATE)`, x = date))+geom_point()
```
more accidents happens in 2017-2019 than 2014-2017

```{r cartype}
summary(data$VEHICLE.TYPE.CODE.1)
```
SUV has the most number of accidents (this could be explained by the number of SUV in New York);
There are duplicated names in levels(e.g. suv, taxi);

```{r borough}
summary(data$BOROUGH)
```
bronx has way more car accidents than other districts.

```{r reason}
summary(data$CONTRIBUTING.FACTOR.VEHICLE.1)
```

## Geographical Analysis

### Mapdeck 

```{r example}
set_token(Sys.getenv("MAPBOX"))
crash_data = read.csv("https://git.io/geocompr-mapdeck")
crash_data = na.omit(crash_data)
ms = mapdeck_style("dark")
mapdeck(style = ms, pitch = 45, location = c(0, 52), zoom = 4) %>%
add_grid(data = crash_data, lat = "lat", lon = "lng", cell_size = 1000,
         elevation_scale = 50, layer_id = "grid_layer",
         colour_range = viridisLite::plasma(6))
head(crash_data)
```

```{r mapdeck}
NYCcrash = data_20172018%>%select("lng" = "LONGITUDE","lat"="LATITUDE")
NYCcrash = na.omit(NYCcrash)
key <- "pk.eyJ1IjoiZ2VvcmdlbGVlMjAxOSIsImEiOiJjazMyZTV1Z3UwajMwM21wbXFpbjdjN2E1In0.FxeN5dw--xCWmVSwMDH4BA"
mapdeck(token = key, style = 'dark',pitch = 45, location = c(0,52), zoom = 4)%>%
  add_grid(data = NYCcrash, lat = 'lat', lon = 'lng',cell_size = 500, elevation_scale = 100, layer_id = "grid_layer2", colour_range = viridisLite::plasma(6))
```

```{r example2}
df <- read.csv(paste0(
'https://raw.githubusercontent.com/uber-common/deck.gl-data/master/',
'examples/3d-heatmap/heatmap-data.csv'
))

mapdeck( token = key, style = mapdeck_style("dark"), pitch = 45 ) %>%
add_grid(
  data = df
  , lat = "lat"
  , lon = "lng"
  , cell_size = 5000
  , elevation_scale = 50
  , layer_id = "grid_layer"
)
```

### Plotly

```{r plotly_example}
token <- "pk.eyJ1IjoiZ2VvcmdlbGVlMjAxOSIsImEiOiJjazMyZTV1Z3UwajMwM21wbXFpbjdjN2E1In0.FxeN5dw--xCWmVSwMDH4BA"
us_cities = read.csv("https://raw.githubusercontent.com/plotly/datasets/master/us-cities-top-1k.csv")

p <- us_cities %>%
  plot_ly(
    lat = ~lat,
    lon = ~lon,
    marker = list(color = "fuchsia"),
    type = 'scattermapbox',
    hovertext = us_cities[,"City"]) %>%
  layout(
    mapbox = list(
      style = 'dark',
      accesstoken = token,
      zoom =2.5,
      center = list(lon = -88, lat = 34)))
#chart_link = api_create(p, filename="dark-tile",username = "SafeguardLi")
#chart_link
p
```

```{r crashdata}
token <- "pk.eyJ1IjoiZ2VvcmdlbGVlMjAxOSIsImEiOiJjazMyZTV1Z3UwajMwM21wbXFpbjdjN2E1In0.FxeN5dw--xCWmVSwMDH4BA"

p <- crash[1:100000,] %>%
  plot_ly(
    lat = ~lat,
    lon = ~lon,
    type = 'densitymapbox',
    coloraxis = 'coloraxis',
    #hovertext = crash[,"victims"],
    radius = 10,
    zauto = TRUE,
    opacity = 0.5) %>%
  layout(
    mapbox = list(
      style = 'dark',
      accesstoken = token,
      zoom =10,
      center = list(lat = 40.712, lon = -74.00)),
    coloraxis = list(colorscale = "Viridis"))
p
```

```{r}
?map_data
p <- plot_ly(
    lat = ~lat,
    lon = ~lon,
    type = 'densitymapbox',
    coloraxis = 'coloraxis',
    #hovertext = crash[,"victims"],
    radius = 10,
    zauto = TRUE,
    opacity = 0.5)%>%
  add_markers(
    x = ~lon, 
    y = ~lat, 
    size = ~pop, 
    color = ~q, 
    hoverinfo = "text",
    text = ~paste(df$name, "<br />", df$pop/1e6, " million")
  )%>%layout(mapbox = list(
      style = 'dark',
      accesstoken = token,
      zoom =10,
      center = list(lat = 40.712, lon = -74.00)),
    coloraxis = list(colorscale = "Viridis"))
p

```


### GGmap

```{r ggmap example}
# load the data
tartu_housing <- read.csv("data/tartu_housing_xy_wgs84_a.csv", sep = ";")
 
# Download the base map
tartu_map_g_str <- get_map(location = "tartu", zoom = 13, source = "osm")
# Draw the heat map
ggmap(tartu_map_g_str, extent = "device") + geom_density2d(data = tartu_housing, aes(x = lon, y = lat), size = 0.3) + 
  stat_density2d(data = tartu_housing, 
                 aes(x = lon, y = lat, fill = ..level.., alpha = ..level..), size = 0.01, 
                 bins = 16, geom = "polygon") + scale_fill_gradient(low = "green", high = "red") + 
  scale_alpha(range = c(0, 0.3), guide = FALSE)
```

### Mapdeck

```{r mapdeck}
key <- "pk.eyJ1IjoiZ2VvcmdlbGVlMjAxOSIsImEiOiJjazMyZTV1Z3UwajMwM21wbXFpbjdjN2E1In0.FxeN5dw--xCWmVSwMDH4BA"
mapdeck(token  = key, style = mapdeck_style('dark'), pitch =45,zoom = 100)%>%add_screengrid(
  data = sf
  , weight = "weight"
  , cell_size = 15
  , layer_id = "gridscreen_layer"
  , opacity = 0.5
)
```

```{r test}
mapdeck(token  = key, style = mapdeck_style('dark'), pitch =45,zoom = 100)%>%add_hexagon(data = victim_dist,
              lat = "lat", 
              lon = "lon",
              focus_layer = TRUE,
              elevation_scale = 10,#sf$victims, 
              layer_id = "heatmap_layer", 
              radius = 300, 
              colour_range = colourvalues::colour_values(1:6, palette = colourvalues::get_palette("viridis")[70:256,]))
  
```

```
add_grid(
  data = victim_dist
  , cell_size = 300
  , elevation_scale = 2
  , layer_id = "grid_layer"
  , auto_highlight = TRUE
)

add_screengrid(
  data = sf
  , weight = "weight"
  , cell_size = 15
  , layer_id = "grid_layer"
)

add_hexagon(data = sf,
              lat = "lat", 
              lon = "lon",
              focus_layer = TRUE,
              elevation_scale = 10,#sf$victims, 
              layer_id = "heatmap_layer", 
              radius = 500, 
              colour_range = colourvalues::colour_values(1:6, palette = colourvalues::get_palette("viridis")[70:256,]))

## need hover info

## need to tune radius automatically

## could reflect info like injuries and dealth.

## Show how the plot changes as time, victims, or season changes.

## We need SHINY!!
?add_hexagon
```

- SHINY

- use map to show injuries distribution

- use map to show contributed factior distribution

- use map to show accident distribution at different time and seasons

- 

### tmap

```{r bubbleplot}
#tmap_mode("plot")
#tm1 <- tm_shape(sf[1000,]) + tm_bubbles(size = "victims")
#tm1
```

### leaflet

```{r test}
?addCircleMarkers
leaflet(sf[0:50,])%>%addTiles()%>%addCircleMarkers(
    radius = sf$victims,
    stroke = FALSE, fillOpacity = 0.5
  )
```

